Hochschild cohomology of torus-equivariant D-modules

### 2017-05-24 paper.tex
Stronger condition on good stacks.

\renewcommand\ls[1]{\mathbfcal{L} #1}
\newcommand\lsY[1]{\mathbfcal{L}_{\stack Y} #1}
\newcommand\cls[1]{\overline{\mathbfcal{L}} #1}
\newcommand\clsY[1]{\overline{\mathbfcal{L}}_{\stack Y} #1}
\newcommand\lsc[1]{\mathbfcal{L}^c #1}
\newcommand\lscY[1]{\mathbfcal{L}_{\stack Y}^c #1}

@@

\newcommand\goodstack{good}
\newcommand\Goodstack{Good}
\newcommand\goodness{goodness}

@@

Let $\stack X = X/G$ be a quotient stack as before.
For any morphism of stacks $h\colon \stack Y → \stack X$ we set $\lsY{\stack X} = \stack X ×_{\stack X × \stack X} \stack Y$.
Thus we have the Cartesian diagram
\[
    \begin{tikzcd}
        \lsY \stack X \arrow[r, "q_{\stack Y}"] \arrow[d] & \stack X \arrow[d, "Δ"] \\
        \stack Y \arrow[r, "Δ∘h"] & \stack X × \stack X
    \end{tikzcd}
\]
Let us fix a relative compactification $\shortbar Δ \colon \bar{\stack X} → \stack X × \stack X$ as in Section~\ref{sec:base-change:compactification}.
Using the notation of Section~\ref{sec:base-change:cone} we set $\clsY{\stack X} = \bar{\stack X} ×_{\stack X × \stack X} \stack Y$ and $\lscY{\stack X} = {\stack X}^c ×_{\stack X × \stack X} \stack Y$.
We let $\bar q_{\stack Y}\colon \clsY\stack X → \bar{\stack X}$ be the projection morphism and $i_{\stack Y}\colon \lscY\stack X \hookrightarrow \clsY\stack X$ the inclusion.
Thus we have the following diagram which is central to remainder of this paper.
\[
    \begin{tikzcd}
        \lsY\stack X \arrow[r, hook] \arrow[d, "q_{\stack Y}"] & \clsY\stack X \arrow[d, "\bar q_{\stack Y}"] & \lscY\stack X \arrow[l, hook', "i_{\stack Y}"'] \arrow[d] \\
        \stack X \arrow[r, hook, "j"] & \bar{\stack X} & \stack X^c \arrow[l, hook']
    \end{tikzcd}
\]
Motivated by Lemma~\ref{lem:base-change-criterion} we make the following definition.

\begin{Def}\label{def:good}
    A quotient stack $\stack X = X/G$ is called \emph{\goodstack} if for every quotient stack $\stack Y = Y/G$ and schematic morphism $\stack Y → \stack X$ the functor $i_{\stack Y}^* \bar q_{\stack Y}^! j_!$ vanishes on $\catDModHol{\stack X}$.
\end{Def}

We will show in Section~\ref{sec:torus} that any stack of the form $\rquot{X}{\Gm^n}$ is \goodstack.
Theorem~\ref{thm:main} then immediately follows from the following theorem which lets us compute the Hochschild cohomology of $\catDMod{\stack X}$ for \goodstack\ quotient stacks.

\begin{Thm}\label{thm:good-is-good}
    If $\stack X = X/G$ is \goodstack, then there exists a canonical structure of monad on $p_{2,!}p₁^!$ and the morphism $p_{2,!}p₁^! → Δ^!Δ_!$ is an isomorphism of monads.
    In particular there is an isomorphism of algebras
    \[
        \HCoh\bigl(\catDMod{\stack X}\bigr)
        \cong
        \opalg{\GammadR\bigl(\stack X,\, p_{2,!} p₁^! k_{\stack X}\bigr)}.
    \]
\end{Thm}

\begin{proof}
    We apply Lemma~\ref{lem:pre:groupoid_monad_hol} to the groupoid induced by $Δ\colon \stack X → \stack X × \stack X$.
    Thus we let $\stack G_\cx$ be the simplicial stack with
    \[
        \stack G_i = \underbrace{\stack X \mathop{×}\limits_{\stack X × \stack X} \dotsb \mathop{×}\limits_{\stack X × \stack X} \stack X}_{\text{$i+1$ factors}}.
    \]
    Setting $\stack Y = \stack X$ in Definition~\ref{def:good} it follows from Lemma~\ref{lem:base-change-criterion} that base change holds along the square
    \[
        \begin{tikzcd}
            \stack G₁ \arrow[r, "p_s"] \arrow[d, "p_t"] & \stack G₀ \arrow[d, "f"] \\
            \stack G₀ \arrow[r, "f"] & \stack X × \stack X
        \end{tikzcd}
    \]
    Let $F\colon [n] → [m]$ be a morphism in $\cat{Δ}^{\mathrm{op}}$ and consider the induced diagram
    \[
        \begin{tikzcd}
            \stack G_{n+1} \arrow[d] \arrow[r] & \stack G_{m+1} \arrow[d] \arrow[r] & \stack X \arrow[d, "Δ"] \\
            \stack G_{n} \arrow[r] & \stack G_m \arrow[r] & \stack X × \stack X
        \end{tikzcd}
    \]
    We note that $\stack G_{m+1} = \stack G_m ×_{\stack X × \stack X} \stack X$ and similarly for $\stack G_n$.
    Thus a relative compactification of $\stack G_{m+1} → \stack G_m$ is given by $\stack G_m ×_{\stack X × \stack X} \bar{\stack X} → \stack G_m$.
    The map $j$ then identifies as the inclusion of $\stack G_m ×_{\stack X × \stack X} \stack X$.
    We have to show that base change holds along the left-hand square.
    But by the assumption and Lemma~\ref{lem:base-change-criterion}, base change holds along the outer rectangle and the right-hand square.
    Thus it also holds along the left-hand square.
\end{proof}

\begin{Rem}
    We expect that most quotient stacks are not \goodstack.
    For example, a direct computation shows that Theorem~\ref{thm:main} does not hold for the stack $\ps1/\Ga$, and hence it is not \goodstack.
    For non-\goodstack\ stacks, the sheaf $i_{\stack X}^* \bar q_{\stack X}^! j_! k_{\stack X}$ instead gives a measurement for the failure of the naive expectation for $\HCoh\bigl(\catDMod{\stack X}\bigr)$.
\end{Rem}

We finish this section with some useful observations for proving that a stack is \goodstack.

\begin{Lem}
    If $\stack X₁ = X₁/G₁$ and $\stack X₂ = X₂/G₂$ are \goodstack, then $\stack X₁ × \stack X₂$ is \goodstack.
\end{Lem}

\begin{proof}
    This follows from compatibility of $i_{\stack Y}^*\bar{q}_{\stack Y}^!j_!$ with $\boxtimes$ and coproducts.
    (Note that $\lscY{(\stack X₁ × \stack X₂)} = \lscY \stack{X₁} × \clsY \stack{X₂} ∪ \clsY{\stack X₁} × \lscY{\stack X₂}$.)
\end{proof}

\begin{Lem}
    Let $U$ be a $G$-equivariant open subset of $X$.
    If $X/G$ is \goodstack\ then $U/G$ is \goodstack.
\end{Lem}

\begin{proof}
    Let $\stack U = U/G$ and let $\stack Y$ be a quotient stack mapping into $\stack U$ (and hence also into $\stack X$).
    Consider the diagram
    \begin{equation}
        \label{eq:lem:cover:diagram}
        \begin{tikzcd}
            \lscY \stack U \arrow[r, hook, "i_{\stack U, \stack Y}"] \arrow[d, hook, "α"] & \clsY{\stack U} \arrow[r, "\bar q_{\stack U,\stack Y}"] \arrow[d, hook, "β"] & \bar{\stack U} \arrow[d, hook, "γ"] & \stack U \arrow[l, hook', "j_{\stack U}"'] \arrow[d, hook, "δ"] \\
            \lscY \stack X \arrow[r, hook, "i_{\stack X, \stack Y}"]                      & \clsY{\stack X} \arrow[r, "\bar q_{\stack X,\stack Y}"]                      & \bar{\stack X}                      & \stack X \arrow[l, hook', "j_{\stack X}"']
        \end{tikzcd}
    \end{equation}
    The vertical arrows are open embeddings and all squares are Cartesian (where we use the same compactification of $G$ for $\bar{\stack X}$ and $\bar{\stack U}$).
    Thus
    \begin{equation*}
        i_{\stack U, \stack Y}^* \bar q_{\stack U,\stack Y}^! j_{\stack U,!} =
        i_{\stack U, \stack Y}^* \bar q_{\stack U,\stack Y}^! j_{\stack U,!} δ^* δ_*=
        α^* i_{\stack X, \stack Y}^* \bar q_{\stack X, \stack Y}^! j_{\stack X,!} δ_* =
        0.
        \qedhere
    \end{equation*}
\end{proof}

The same argument can be used to reduce the computation to a smooth cover.
We will now introduce notation for the special case of the cover $\bar Γ → \bar{\stack X}$.
The corresponding covers of the other relevant stacks are introduced in the following diagram with Cartesian squares.
\begin{equation}
    \label{eq:base-change:scheme-cover}
    \begin{tikzcd}
        \schemelscY \stack X \arrow[r, hook, "\schemei_{\stack Y}"] \arrow[d] & \schemeclsY \stack X \arrow[r, "\schemebarq_{\stack Y}"] \arrow[d] & \bar Γ \arrow[d] & Γ \arrow[l, hook', "\schemej"'] \arrow[d] \\
        \lscY \stack X \arrow[r, hook, "i_{\stack Y}"]                        & \clsY \stack X \arrow[r, "\bar q_{\stack Y}"]                       & \bar{\stack X}   & \stack X \arrow[l, hook', "j"']
    \end{tikzcd}
\end{equation}
We note that all vertical morphisms are smooth and the spaces in the top row are schemes.
Let $\schemeh\colon X → Y$ be the $G$-equivariant morphism of schemes inducing $h$ on quotient stacks.
Then the scheme $\schemeclsY \stack X$ is given by
\[
    \schemeclsY \stack X =
    \biggl\{
        \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y × \bar G : \bigl(g₂,\, \schemeh(y),\, g₁\schemeh(y)\bigr) ∈ \bar Γ
    \biggr\}.
\]

\begin{Lem}\label{lem:base-change:scheme-cover}
    A stack $X/G$ is \goodstack\ if and only if for each morphism $Y/G → X/G$ the composition $(\schemei_{\stack Y})^* (\schemebarq_{\stack Y})^! \schemej_!$ vanishes on $\catDModHolMon{Γ}{G×G}$.
\end{Lem}

\begin{proof}
    This follows from the fact that pullback along the smooth vertical morphisms in \eqref{eq:base-change:scheme-cover} is conservative \cite[Lemma~5.1.6]{DrinfeldGaitsgory:2013:FinitenessQuestions} and commutes with the other morphisms up to a shift.
\end{proof}

\begin{Lem}
    \label{lem:base-change:cover}%
    If there exists a $G$-stable open cover $U_i$ of $X$ such that all stacks $U_i/G$ are \goodstack, then $X/G$ is \goodstack.
\end{Lem}

\begin{proof}
    Let $\stack U_i = U_i/G$ be the corresponding quotient stacks.
    We first show that the stacks $\lscY{\stack U_i}$ form an open cover of $\lscY{\stack X}$\footnote{
        This is not completely obvious, since the $\bar{\stack U}_i$ do not necessarily form a cover of $\bar{\stack X}$.
        For example, consider $\ps1$ with the usual linear $\Gm$-action and the usual affine cover.
    }.
    For this it suffices to show that the open subschemes $\schemeclsY \stack U_i$ cover $\schemeclsY \stack X$.
    Let $(g₁, y, g₂)$ be a point of $\schemeclsY \stack X$.
    Then there exists some $U_i$ with $h'(y) ∈ U_i$.
    But then $g₁h'(y)$ is also in $U_i$ and hence $(h'(y), g₂, g₁h'(y)) ∈ \bar{\stack U}_i$.
    Thus $(g₁, y, g₂)$ is in $\schemeclsY \stack U_i$.

    It now suffices to show that the restrictions of $i_{\stack Y}^*\bar{q}_{\stack Y}^!j_! \sheaf F$ to $\lscY{\stack U_i}$ vanish for every $\sheaf F ∈ \catDMod{\stack X}$.
    But this follows from the diagram~\eqref{eq:lem:cover:diagram} (for $\stack U_i$ instead of $\stack U$) and the \goodness\ of $\stack U_i$.
\end{proof}

>>>>

\newcommand\XXtimes{%
    \mathchoice%
        {\mathop{×}\limits_{\stack X × \stack X}}
        {×_{\stack X × \stack X}}
        {×_{\stack X × \stack X}}
        {×_{\stack X × \stack X}}
    }
\renewcommand\ls[1]{\mathbfcal{L} #1}
\newcommand\lsY[2][\stack Y]{\mathbfcal{L}_{#1} #2}
\newcommand\cls[1]{\overline{\mathbfcal{L}} #1}
\newcommand\clsY[2][\stack Y]{\overline{\mathbfcal{L}}_{#1} #2}
\newcommand\lsc[1]{\mathbfcal{L}^c #1}
\newcommand\lscY[2][\stack Y]{\mathbfcal{L}_{#1}^c #2}

\newcommand\sls[1]{L#1}
\newcommand\slsY[2][\stack Y]{L_{#1}#2}
\newcommand\scls[1]{\overline{L}#1}
\newcommand\sclsY[2][\stack Y]{\overline{L}_{#1}#2}
\newcommand\slsc[1]{L^c #1}
\newcommand\slscY[2][\stack Y]{L^c_{#1}#2}

@@

\newcommand\goodstack{XXXgoodXXX}
\newcommand\Goodstack{XXXGoodXXX}
\newcommand\goodness{property \textbf{(!)}}
\newcommand\goodnessshort{\textbf{(!)}}
\newcommand\isgood{has property \textbf{(!)}}
\newcommand\aregood{have property \textbf{(!)}}
\newcommand\isnotgood{does not have property \textbf{(!)}}
\newcommand\arenotgood{do not have property \textbf{(!)}}
\newcommand\goodX[1]{#1 with property \textbf{(!)}}
\newcommand\goodnessb{property \textbf{(!')}}
\newcommand\goodnessbshort{\textbf{(!')}}
\newcommand\isgoodb{has property \textbf{(!')}}
\newcommand\aregoodb{have property \textbf{(!')}}
\newcommand\goodbX[1]{#1 with property \textbf{(!')}}

@@

Let $\stack Y$ be a stack over $\stack X$.
To simplify notation, we set
\[
    \lsY = \stack Y \XXtimes \stack X,
\]
where the fiber product is taken over the maps $\stack Y → \stack X \xrightarrow{Δ} \stack X × \stack X$ and $Δ$.
Further if $f\colon \stack Y₁ → \stack Y₂$ is a morphism of stacks over $\stack X$ we write $\ls f$ for the induced morphism $\lsY[\stack Y₁]{\stack X} → \lsY[\stack Y₂]{\stack X}$.

\begin{Def}\label{def:good}
    We say that a quotient stack $\stack X = X/G$ \emph{\isgood} if the following two conditions hold.
    \begin{enumerate}
        \item $!$-base-change holds along the Cartesian square
            \[
                \begin{tikzcd}
                    \ls \stack X \arrow[r, "p₂"] \arrow[d, "p₁"] & \stack X \arrow[d, "Δ"] \\
                    \stack X \arrow[r, "Δ"] & \stack X × \stack X
                \end{tikzcd}
            \]
            i.e.~the canonical morphism $p_{1,!}p₂^! → Δ^!Δ_!$ is an isomorphism on holonomic D-modules.
        \item For any schematic morphism $f\colon \stack Y₁ = Y₁/G → \stack Y₂ = Y₂/G$ of $G$-quotient stacks over $\stack X$, $!$-base-change holds along the Cartesian diagram
            \[
                \begin{tikzcd}
                    \lsY[\stack Y₂]{\stack X} \arrow[r, "\ls f"] \arrow[d, "π₂"] & \lsY[\stack Y₁]{\stack X} \arrow[d, "π₁"]\\
                    \stack Y₂ \arrow[r, "f"] & \stack Y₁
                \end{tikzcd}
            \]
            i.e.~the canonical morphism $π_{2,!}(\ls f)^! → f^! π_{1,!}$ is an isomorphism on holonomic D-modules.
    \end{enumerate}
\end{Def}

We will show in Section~\ref{sec:torus} that any stack of the form $\rquot{X}{\Gm^n}$ \isgood.
Theorem~\ref{thm:main} then immediately follows from the following observation which lets us compute the Hochschild cohomology of $\catDMod{\stack X}$ for \goodX{quotient stacks}.

\begin{Prop}\label{prop:good-is-good}
    If $\stack X = X/G$ \isgood, then there exists a canonical structure of monad on $p_{1,!}p₂^!$ and the morphism $p_{2,!}p₁^! → Δ^!Δ_!$ is an isomorphism of monads.
    In particular there is an isomorphism of algebras
    \[
        \HCoh\bigl(\catDMod{\stack X}\bigr)
        \cong
        \opalg{\GammadR\bigl(\stack X,\, p_{1,!} p₂^! k_{\stack X}\bigr)}.
    \]
\end{Prop}

\begin{proof}
    We apply Lemma~\ref{lem:pre:groupoid_monad_hol} to the groupoid induced by $Δ\colon \stack X → \stack X × \stack X$.
    Thus we let $\stack G_\cx$ be the simplicial stack with
    \[
        \stack G_i = \underbrace{\stack X \mathop{×}\limits_{\stack X × \stack X} \dotsb \mathop{×}\limits_{\stack X × \stack X} \stack X}_{\text{$i+1$ factors}}.
    \]
    The second base change condition of Lemma~\ref{lem:pre:groupoid_monad_hol} holds by definition.
    Let $F\colon [n] → [m]$ be a morphism in $\cat{Δ}^{\mathrm{op}}$ and consider the induced diagram
    \[
        \begin{tikzcd}
            \stack G_{n+1} \arrow[d] \arrow[r] & \stack G_{m+1} \arrow[d] \arrow[r] & \stack X \arrow[d, "Δ"] \\
            \stack G_{n} \arrow[r] & \stack G_m \arrow[r] & \stack X × \stack X
        \end{tikzcd}
    \]
    We note that $\stack G_{m+1} = \stack G_m ×_{\stack X × \stack X} \stack X$ and similarly for $\stack G_n$.
    Thus setting $\stack Y₁ = \stack G_n$ and $\stack Y₂ = \stack G_m$ in the definition of \goodness, we see that all the required base changes holds.
\end{proof}

\begin{Rem}
    We expect that most quotient stacks \arenotgood.
    For example, a direct computation shows that Theorem~\ref{thm:main} does not hold for the stack $\ps1/\Ga$, and hence it \isnotgood.
\end{Rem}

We will use Lemma~\ref{lem:base-change-criterion} in order to check the base change criteria in Definition~\ref{def:good}.
In order to do so we unfortunately have to introduce some additional notation.
Let us fix a compactification $\bar G$ of $G$ and a relative compactification $\stack X \xrightarrow{j} \bar{\stack X} \xrightarrow{\bar Δ} \stack X × \stack X$ as in Section~\ref{sec:base-change:compactification}.
For any $\stack Y → \stack X$ this induces a relative compactification $\clsY{\stack X} = \stack Y \XXtimes \bar{\stack X}$.
Let us write $j_{\stack Y}\colon \lsY{\stack X} \hookrightarrow \clsY{\stack X}$ for the open inclusion and $i_{\stack Y}\colon \lscY{\stack X} = \stack Y \XXtimes \stack X^c → \clsY{\stack X}$ for the complement.
Thus we have the following two diagrams with Cartesian squares which are central to the remainder of this paper.
The first describes the situation for a loop stack:
\begin{equation}\label{eq:diag:central1}
    \begin{tikzcd}
        \ls\stack X \arrow[r, "j_{\stack X}", hook] \arrow[d, "p₂"] & \cls\stack X \arrow[d, "\bar p₂"] & \lsc\stack X \arrow[l, hook', "i_{\stack X}"']  \arrow[d] \\
        \stack X \arrow[r, hook, "j"] & \bar{\stack X} & \stack X^c \arrow[l, hook']
    \end{tikzcd}
\end{equation}
For the second let $\stack Y₁ → \stack Y₂$ be a morphism of stacks over $\stack X$:
\begin{equation}\label{eq:diag:central2}
    \begin{tikzcd}
        \lsY[\stack Y₁]{\stack X} \arrow[r, "j_{\stack Y₁}", hook] \arrow[d, "\ls f"] & \clsY[\stack Y₁]{\stack X} \arrow[d, "{\cls f}"] & \lscY[\stack Y₁]{\stack X} \arrow[l, hook', "i_{\stack Y₁}"']  \arrow[d] \\
        \lsY[\stack Y₂]{\stack X} \arrow[r, hook, "j_{\stack Y₂}"] & \clsY[\stack Y₂]{\stack X} & \lscY[\stack Y₂]{\stack X} \arrow[l, hook']
    \end{tikzcd}
\end{equation}
With this setup we make the following definition.
\begin{Def}\label{def:good'}
    We say that a quotient stack $\stack X = X/G$ \emph{\isgoodb} if the following two conditions hold.
    \begin{enumerate}
        \item $i_{\stack X}^* \bar p₂^! j_!$ vanishes on $\catDModHol{\stack X}$.
        \item For any schematic morphism $f\colon \stack Y₁ → \stack Y₂$ of $G$-quotient stacks over $\stack X$ the composition $i_{\stack Y₁}^* (\bar{\ls f})^! j_{\stack Y₂,!}$ vanishes on $\catDModHol{\lsY[\stack Y₂]{\stack X}}$.
    \end{enumerate}
\end{Def}

Lemma~\ref{lem:base-change-criterion} says that $\goodnessbshort$\ implies $\goodnessshort$.
In the remainder of this section we will discuss several reduction steps for showing that a given stack \isgoodb.

%\begin{Lem}
%    If $\stack X₁ = X₁/G₁$ and $\stack X₂ = X₂/G₂$ are \goodstack, then $\stack X₁ × \stack X₂$ is \goodstack.
%\end{Lem}
%
%\begin{proof}
%    This follows from compatibility of $i_{\stack Y}^*\bar{q}_{\stack Y}^!j_!$ with $\boxtimes$ and coproducts.
%    (Note that $\lscY{(\stack X₁ × \stack X₂)} = \lscY \stack{X₁} × \clsY \stack{X₂} ∪ \clsY{\stack X₁} × \lscY{\stack X₂}$.)
%\end{proof}

\begin{Lem}
    Let $U$ be a $G$-equivariant open subset of $X$.
    If $X/G$ \isgoodb\ then $U/G$ \isgoodb.
\end{Lem}

\begin{proof}
    Set $\stack U = U/G$.
    We will only show the second condition of Definition~\ref{def:good'}, the first one is similar.
    Thus let $f\colon \stack Y₁ → \stack Y₂$ be a map of quotient stacks over $\stack U$ (and hence also over $U$).
    We note that since $\stack U$ is an open subset we have isomorphisms $\lsY[\stack Y_i]{\stack U} \cong \stack Y_i \XXtimes \stack U$.
    Consider the diagram
    \begin{equation}
        \label{eq:lem:cover:diagram}
        \begin{tikzcd}
            \lsY[\stack Y₂]{\stack U} \arrow[r, hook, "j_{\stack Y₂}^{\stack U}"] \arrow[d, hook, "α"] &
            \clsY[\stack Y₂]{\stack U} \arrow[d, hook, "β"] &
            \clsY[\stack Y₁]{\stack U} \arrow[l, "{\cls f}^{\stack U}"'] \arrow[d, hook, "γ"] &
            \lscY[\stack Y₁]{\stack U} \arrow[l, hook', "i^{\stack U}_{\stack Y₁}"'] \arrow[d, hook, "δ"] \\
            %
            \lsY[\stack Y₂]{\stack X} \arrow[r, hook, "j_{\stack Y₂}^{\stack X}"] &
            \clsY[\stack Y₂]{\stack X} &
            \clsY[\stack Y₁]{\stack X} \arrow[l, "{\cls f}^{\stack X}"'] &
            \lscY[\stack Y₁]{\stack X} \arrow[l, hook', "i^{\stack X}_{\stack Y₁}"']
        \end{tikzcd}
    \end{equation}
    The vertical arrows are open embeddings and all squares are Cartesian (where we use the same compactification of $G$ for $\bar{\stack X}$ and $\bar{\stack U}$).
    Thus
    \begin{equation*}
        i^{\stack U,*}_{\stack Y₁} {\cls f}^{\stack U,!} j_{\stack Y₂,!}^{\stack U} =
        i^{\stack U,*}_{\stack Y₁} {\cls f}^{\stack U,!} j_{\stack Y₂,!}^{\stack U} α^* α_*=
        δ^* i^{\stack X,*}_{\stack Y₁} {\cls f}^{\stack U,!} j_{\stack Y₂,!}^{\stack X} α_*=
        0.
        \qedhere
    \end{equation*}
\end{proof}

A similar can be used to reduce the computation to a smooth cover.
In particular we will want to reduce to computations on a schematic cover.
On such a cover we will use primes to indicate maps on schemes and will use $\schemels{}$ instead of $\ls{}$ for the covers of the loop spaces.
If we start with the cover $\bar Γ → \bar{\stack X}$, the pullbacks to the part of diagram \eqref{eq:diag:central1} of interest are
\begin{equation}
    \label{eq:diag:scheme-cover1}
    \begin{tikzcd}
        Γ \arrow[r, hook, "j'"] \arrow[d] &
        \bar Γ \arrow[d] &
        \scls \stack X \arrow[l, "\bar p₂'"'] \arrow[d] &
        \slsc \stack X \arrow[l, hook', "i_{\stack X}'"'] \arrow[d]\\
        %
        \stack X \arrow[r, hook, "j"] &
        \bar{\stack X} &
        \cls \stack X \arrow[l, "\bar p₂"'] &
        \lsc \stack X \arrow[l, hook', "i_{\stack X}"']
    \end{tikzcd}
\end{equation}
Similarly, the interesting parts of diagram \eqref{eq:diag:central2} become
\begin{equation}
    \label{eq:diag:scheme-cover2}
    \begin{tikzcd}
        \slsY[\stack Y₂]{\stack X} \arrow[r, hook, "j_{\stack Y₂}'"] \arrow[d] &
        \sclsY[\stack Y₂]{\stack X} \arrow[d] &
        \sclsY[\stack Y₁]{\stack X} \arrow[l, "\schemecls f"'] \arrow[d] &
        \slscY[\stack Y₁]{\stack X} \arrow[l, hook', "i_{\stack Y₁}'"'] \arrow[d]\\
        %
        \lsY[\stack Y₂]{\stack X} \arrow[r, hook, "j_{\stack Y₂}"] &
        \clsY[\stack Y₂]{\stack X} &
        \clsY[\stack Y₁]{\stack X} \arrow[l, "\cls f"'] &
        \lscY[\stack Y₁]{\stack X} \arrow[l, hook', "i_{\stack Y₁}"']
    \end{tikzcd}
\end{equation}
In both diagrams all vertical morphisms are smooth and the spaces in the top row are schemes.
Explicitly, if $h'\colon Y → X$ is a $G$-equivariant morphism of schemes inducing the structure map $\stack Y → \stack X$, then
\[
    \sclsY \stack X =
    \biggl\{
        \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y × \bar G : \bigl(g₂,\, \schemeh(y),\, g₁\schemeh(y)\bigr) ∈ \bar Γ
    \biggr\}.
\]

\begin{Lem}\label{lem:base-change:scheme-cover}
    A stack $X/G$ \isgoodb\ if and only if the following two conditions hold:
    \begin{enumerate}
        \item The composition $(i_{\stack X}')^*(\bar p₂')^! j'_!$ vanishes on $\catDModHolMon{Γ}{G×G}$.
        \item For each equivariant morphism $f'\colon Y₁ → Y₂$ of $G$-schemes the composition $(i_{\stack Y₁}')^*(\scls f)^! j'_{\stack Y₂,!}$ vanishes on $\catDModHolMon{\slsY[\stack Y₂]{\stack X}}{G×G}$.
    \end{enumerate}
\end{Lem}

\begin{proof}
    This follows from the fact that pullback along the smooth vertical morphisms in \eqref{eq:diag:scheme-cover1} and \eqref{eq:diag:scheme-cover2} is conservative \cite[Lemma~5.1.6]{DrinfeldGaitsgory:2013:FinitenessQuestions} and commutes with the other morphisms up to a shift.
\end{proof}

\begin{Lem}
    \label{lem:base-change:cover}%
    If there exists a $G$-stable open cover $U_i$ of $X$ such that all stacks $U_i/G$ \aregoodb, then $X/G$ \isgoodb.
\end{Lem}

\begin{proof}
    Let $\stack U_i = U_i/G$ be the corresponding quotient stacks.
    We will again only show the second condition, the first being simpler.

    Let us first show that for any $\stack Y → \stack X$ the stacks $\lscY{\stack U_i}$ form an open cover of $\lscY{\stack X}$\footnote{
        This is not completely obvious, since the $\bar{\stack U}_i$ do not necessarily form a cover of $\bar{\stack X}$.
        For example, consider $\ps1$ with the usual linear $\Gm$-action and the usual affine cover.
    }.
    For this it suffices to show that the open subschemes $\sclsY \stack U_i$ cover $\sclsY \stack X$.
    Let $(g₁, y, g₂)$ be a point of $\sclsY \stack X$.
    Then there exists some $U_i$ with $h'(y) ∈ U_i$.
    But then $g₁h'(y)$ is also in $U_i$ and hence $(h'(y), g₂, g₁h'(y)) ∈ \bar{\stack U}_i$.
    Thus $(g₁, y, g₂)$ is in $\sclsY \stack U_i$.

    It now suffices to show that the restrictions of $i_{\stack Y₁}^*\cls{f}^!j_{\stack Y₂,!} \sheaf F$ to $\lscY[\stack Y₁]{\stack U_i}$ vanish for every $\sheaf F ∈ \catDModHol{\lsY[\stack Y₂]{\stack X}}$.
    But this follows from the diagram~\eqref{eq:lem:cover:diagram} (for $\stack U_i$ instead of $\stack U$) and the assumption on $\stack U_i$.
\end{proof}

-------------
